---
title: "Conceptualizations of the TPCK-Framework"
author:
- affiliation: University of Tübingen
  email: armin.fabian@uni-tuebingen.de
  name: Armin Fabian
  url: https://uni-tuebingen.de/de/175743
- affiliation: University of Tübingen
  email: iris.backfisch@uni-tuebingen
  name: Iris Backfisch
  url: https://uni-tuebingen.de/de/169665
- affiliation: University of Tübingen
  email: andreas.lachner@uni-tuebingen.de
  name: Andreas Lachner
  url: https://uni-tuebingen.de/de/169665
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    highlight: espresso
    number_sections: yes
    theme: paper
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
description: "Synthesized from  \n"
css: www/style.css
---

```{r setup, echo=F, message=F, warning=F, comment=F}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(pander)
library(dplyr)
library(kableExtra)
```

\
\
\

<div style="padding: 5px; background-color: #F0F0F0;">
__This is__ a Rmd-template for protocols and reporting of systematic reviews and meta-analyses. It synthesizes three sources of standards:

* [PRISMA-P](https://doi.org/10.1136/bmj.i4086)
* [PROSPERO](https://www.crd.york.ac.uk/prospero/)
* [MARS](https://doi.org/10.1037/amp0000389)

The template is __aimed at__

* guiding the process of planning the systemtic review/ meta-analysis
* providing a form for preregistration (enter your text, export as standalone html, upload as preregistration)

We are aware that MARS targets aspects of reporting after the systemtic review/ meta-analysis is completed rather than decisions and reasoning in the planning phase as PRISMA-P and PROSPERO. MARS nevertheless provides a good framework to determine crucial points for systemtic reviews/ meta-analyses to be addressed as early as in the planning phase.
</div>

  
_Standards have been partially adapted. Click 'show changes' to see changes and reasons for change._  

<button data-toggle="collapse" data-target="#changes">show changes</button>
<div id="changes" class="collapse">
| standard |  implemented change  | reason                      |
|:---------|:---------------------|:----------------------------|
| MARS |  Left out paper section "Abstract"  |  An abstract is important for reporting, not however, for planning and registering. |
| MARS |  Left out paper section "Results" and parts of "Discussion"  |  Specifications on how to report results is important for reporting, not however, for planning and registering. Prospective information on how results will be computed/ synthesized is preserved. |
| MARS | Left out "Protocol: List where the full protocol can be found" | This form practically is the protocol. |
|  PROSPERO  |  Left out non-mandatory fields or integrated them with mandatory fields.  |  Avoiding too detailed specifications. All relevant informations will be integrated. |
| PROSPERO | Left out some options in "Type and method of review" | Options left out are purely health/ medicine related. |
| PROSPERO | Left out "Health area of the review" | This field is purely health/ medicine related. |


</div>

\
\
\


# General 

## Working Title

<button data-toggle="collapse" data-target="#wt">show sources</button>
<div id="wt" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Identify the report as a protocol of a systematic review. If the protocol is for an update of a previous systematic review, identify as such",
                                            # PROSPERO
                                            "Give the working title of the review, for example the one used for obtaining funding. Ideally the title should state succinctly the interventions or exposures being reviewed and the associated health or social problems. Where appropriate, the title should use the PI(E)COS structure to contain information on the Participants, Intervention (or Exposure) and Comparison groups, the Outcomes to be measured and Study designs to be included.

For reviews in languages other than English, this field should be used to enter the title in the language of the
review. This will be displayed together with the English language title.",
                                            # MARS
                                            "Title: State the research question and type of research synthesis (e.g., narrative synthesis, meta-analysis)"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

Bringing Light Into the Dark: A Systematic Review on the Diverse Conceptualizations of the TPCK Framework


## Type of Review

<button data-toggle="collapse" data-target="#typeor">show sources</button>
<div id="typeor" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Type and method of review: Select the type of review and the review method from the lists below. Select the health area(s) of interest for your review.

* Meta-analysis
* Narrative synthesis
* Network meta-analysis
* Review of reviews
* Synthesis of qualitative studies
* Systematic review
* Other",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

Systematic Review



## Link to Registration

<button data-toggle="collapse" data-target="#ltr">show sources</button>
<div id="ltr" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "If registered, provide the name of the registry (such as PROSPERO) and registration number.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Give the place where the synthesis is registered and its registry number, if registered"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

This form is used as registration


## Anticipated start and completion date

<button data-toggle="collapse" data-target="#aasd">show sources</button>
<div id="aasd" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Give the date when the systematic review commenced, or is expected to commence. Give the date by which the review is expected to be completed.",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

**Start**: October 2020 

**Anticipated Complection Date**: March 2021



## Stage of Review

<button data-toggle="collapse" data-target="#sor">show sources</button>
<div id="sor" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Indicate the stage of progress of the review by ticking the relevant Started and Completed boxes. Additional
information may be added in the free text box provided.
Please note: Reviews that have progressed beyond the point of completing data extraction at the time of
initial registration are not eligible for inclusion in PROSPERO. Should evidence of incorrect status and/or
completion date being supplied at the time of submission come to light, the content of the PROSPERO
record will be removed leaving only the title and named contact details and a statement that inaccuracies in
the stage of the review date had been identified.
This field should be updated when any amendments are made to a published record and on completion and
publication of the review. If this field was pre-populated from the initial screening questions then you are not
able to edit it until the record is published.

* The review has not yet started: [yes/no]

| Review stage | Started | Completed |
|:--------------------------------------------| :----:| :----:|
| Preliminary searches | Yes/No | Yes/No
| Piloting of the study selection process | Yes/No | Yes/No
| Formal screening of search results against eligibility criteria | Yes/No | Yes/No
| Data extraction | Yes/No | Yes/No
| Risk of bias (quality) assessment | Yes/No | Yes/No
| Data analysis | Yes/No | Yes/No

Provide any other relevant information about the stage of the review here (e.g. Funded proposal, protocol not
yet finalised).",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources, escape = F) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

The review has not yet started [yes/no]: no

| Review stage | Started | Completed |
|:--------------------------------------------| :----:| :----:|
| Preliminary searches | Yes | Yes
| Piloting of the study selection process | No | No
| Formal screening of search results against eligibility criteria | No | No
| Data extraction | No | No
| Risk of bias (quality) assessment | No | No
| Data analysis | No | No


## Names, Affiliations, Contact

<button data-toggle="collapse" data-target="#nac">show sources</button>
<div id="nac" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "
* Provide name, institutional affiliation, e-mail address of all protocol authors; provide physical mailing address of corresponding author.
* Describe contributions of protocol authors and identify the guarantor of the review.",
                                            # PROSPERO
                                            "
* Named Contact: The named contact acts as the guarantor for the accuracy of the information presented in the register record.
* Named contact email: Give the electronic mail address of the named contact.
* Organisational affiliation of the review: Full title of the organisational affiliations for this review and website address if available. This field may be completed as 'None' if the review is not affiliated to any organisation.
* Review team members and their organisational affiliations: Give the personal details and the organisational affiliations of each member of the review team. Affiliation refers to groups or organisations to which review team members belong.",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

**Corresponding author**
Armin Fabian
University of Tübingen
https://uni-tuebingen.de/einrichtungen/zentrale-einrichtungen/tuebingen-school-of-education-tuese/personen/mitarbeiterinnen-und-mitarbeiter-qualitaetsoffensive-lehrerbildung-digitalisierung/armin-fabian/
Brunnenstraße 20, 72074 Tübingen

## Collaborators

<button data-toggle="collapse" data-target="#colla">show sources</button>
<div id="colla" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Collaborators (name & affilitation) of individuals working on the review, but are not review team member.",
                                            # MARS
                                            "Not specified."))
# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

* Named contact: Armin Fabian
* Named contact email: armin.fabian@uni-tuebingen.de
* Named contact ORCID: [0000-0001-6493-2147](https://orcid.org/0000-0001-6493-2147)
* Organisational affiliation of the review: University of Tübingen, Germany
* Review team members and their organisational affiliations:
  - Iris Backfisch, i.backfisch@iwm-tuebingen.de,  ORCID [0000-0002-1363-9888](https://orcid.org/0000-0002-1363-9888)
  - Andreas Lachner, andreas.lachner@uni-tuebingen.de, ORCID [0000-0001-5866-7164](https://orcid.org/0000-0001-5866-7164)


## Amendments to previous versions

<button data-toggle="collapse" data-target="#atpv">show sources</button>
<div id="atpv" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "If the protocol represents an amendment of a previously completed or published protocol, identify as such and list changes; otherwise, state plan for documenting important protocol amendments.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

Amendments will be published as new version of the document under the same DOI (or will point to previous version).


## Funding sources, sponsors and their roles

<button data-toggle="collapse" data-target="#fsign">show sources</button>
<div id="fsign" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "
* Indicate sources of financial or other support for the review
* Provide name for the review funder and/or sponsor
* Describe roles of funder(s), sponsor(s), and/or institution(s), if any, in developing the protocol",
                                            # PROSPERO
                                            "Funding sources/sponsors: Give details of the individuals, organizations, groups or other legal entities who take responsibility for initiating, managing, sponsoring and/or financing the review. Include any unique identification numbers assigned to the review by the individuals or bodies listed. Grant numbers.",
                                            # MARS
                                            "
* List all sources of monetary and in-kind funding support
* State the role of funders in conducting the synthesis and deciding to publish the results, if any"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

BMBF - This project is part of the "Qualitätsoffensive Lehrerbildung”, a joint initiative of the Federal Government andthe Länder which aims to improve the quality of teacher training. The programme is funded by the Federal
Ministry of Education and Research. The authors are responsible for the content of this publication.


## Conflict of Interest

<button data-toggle="collapse" data-target="#coi">show sources</button>
<div id="coi" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "List any conditions that could lead to actual or perceived undue influence on judgements concerning the main topic investigated in the review.",
                                            # MARS
                                            "Describe possible conflicts of interest, including financial and other nonfinancial interests."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

No conflict of interest.


# Introduction

## Rationale

<button data-toggle="collapse" data-target="#ram">show sources</button>
<div id="ram" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Describe the rationale for the review in the context of what is already known.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Problem: State the question or relation(s) under investigation, including

* Historical background, including previous syntheses and meta-analyses related to the topic 
* Theoretical, policy, and/or practical issues related to the question or relation(s) of interest
* Populations and settings to which the question or relation(s) is relevant
* Rationale for
   (a) choice of study designs, 
   (b) the selection and coding of outcomes, 
   (c) the selection and coding potential moderators or mediators of results 
* Psychometric characteristics of outcome measures and other variables
"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

When it comes to school or education as such, the discussion about the use of digital media has become ubiquitous. However, recent studies indicate that teachers still rarely use digital technologies for educational purposes, and if they do, they rarely integrate them into teaching in a didactically meaningful manner (Farjon, Smits & Voogt, 2019). One of the main boundary conditions of successful technology integration, that researchers have identified, is the professional knowledge of teachers. Accordingly, to use technologies in classrooms purposefully, teachers need specific knowledge that is tailored around the use of digital technologies. One of the most recited and adopted models used to describe such knowledge is the TPACK (**t**echnological, **p**edagogical **a**nd **c**ontent **k**nowledge) model by Mishra and Koehler (2006). The TPACK model captures the idea of bringing together and connecting basic knowledge components (i.e.  knowledge about technology, pedagogy and content) to form a new central form of knowledge – TPCK (technological, pedagogical and content knowledge. In literature, TPCK has evolved to become *the* central focus of researchers when it comes to knowledge regarding technology integration (Kim & Lee, 2018).

Ever since the introduction of the TPACK model in 2006, numerous researchers have worked *on* the model trying to clarify its underlying structure (Angeli & Valanides, 2009; Graham, 2011); or *with* the model using it as theoretical background for data driven studies (Angeli et al., 2016; Cavanagh & Koehler, 2013;). Yet, to date the question of what TPCK constitutes remains a source of scholarly debate (Petko, 2020). In the authors’ opinion, this is mainly due to the vast, diverse and often seemingly contradictory conceptualisations of TPCK that exist in the TPACK literature. To provide a comprehensive picture on TPCK, it is therefore necessary to understand and organize the different conceptualizations that researchers introduced when working on or with the TPACK model.

Against this background, we conduct a systematic review that attempts to clarify and systematize existing conceptualizations within the huge corpus of TPACK research. More precisely, we are interested in examining if TPACK researchers – in their endeavours of conceptualising TPCK – have put emphasis on specific TPCK components (i.e. subdomains of TPCK: TK, CK, PK, PCK, TCK, TPK and TPCK) while possibly neglecting others. In other words: Which foci lenses have been used by researchers when dealing with the TPACK model? As many researchers demand, a particular focus will here be on *how* and *to what extent* content-specific features of TPCK were accounted for in existing conceptualizations of the TPACK model.

This systematic review will help to organize different approaches that researchers have taken and will take to understand and apply the highly complex framework of TPCK.


__References__

Angeli, C., & Valanides, N. (2009): Epistemological and methodological issues for the conceptualization, development, and assessment of
 ICT-TPCK: Advances in technological pedagogical content knowledge (TPCK). *Computers & Education*, 52 (1), 154–168. doi: 10.1016/j.compedu.2008.07.006. 

Angeli, C.; Voogt, J.; Fluck, A.; Webb, M.; Cox, M.; Malyn-Smith, J.,& Zagani, J. (2016): A K-6 Computational Thinking Curriculum Framework: Implication for Teacher Knowledge. In: *Educational Technology & Society*, 19 (3), 47–57. 

Cavanagh, Robert F.; Koehler, Matthew J. (2013): A Turn toward Specifying Validity Criteria in the Measurement of Technological Pedagogical Content Knowledge (TPACK). *Journal of Research on Technology in Education*, 46 (2), S. 129–148. doi: 10.1080/15391523.2013.10782616.

Cox, S., & Graham, CR (2009). Diagramming TPACK in practice: Using an elaborated model of the TPACK framework to analyze and depict teacher knowledge. *TechTrends: Linking Research & Practice to Improve Learning*, 53 (5), 60-69. 

Farjon, D., Smits, A., & Voogt, J. (2019). Technology integration of student teachers explained by attitudes and beliefs, competency, access, and experience. *Computers & Education*, 130, 81-93. doi: 10.1016/j.compedu.2018.11.010 

Kim, S.-W., & Lee, Y. J. (2018): The Effects of the TPACK-P Educational Program on Teachers’ TPACK: Programming as a Technological Tool. *International Journal of Engineering & Technology*, 30 (7), 636–643. 

Mishra, P., & Koehler, M. J. (2006). Technological pedagogical content knowledge: A framework for integrating technology in teacher knowledge. *Teachers College Record*, 108(6), 1017-1054. 

Petko, D. (2020). Quo vadis TPACK? Scouting the road ahead. *Proceedings of EdMedia + Innovate Learning* (pp. 1349-1358). Online, The Netherlands: Association for the Advancement of Computing in Education (AACE). Retrieved October 10, 2020 from https://www.learntechlib.org/primary/p/217445/. 





## Research Questions

<button data-toggle="collapse" data-target="#rq">show sources</button>
<div id="rq" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Provide an explicit statement of the question(s) the review will address with reference to participants, interventions, comparators, and outcomes (PICO)",
                                            # PROSPERO
                                            "State the question(s) to be addressed by the review, clearly and precisely. Review questions may be specific or broad. It may be appropriate to break very broad questions down into a series of related more specific questions. Questions may be framed or refined using PI(E)COS where relevant.",
                                            # MARS
                                            "Objectives: State the hypotheses examined, indicating which were prespecified, including

* Question in terms of relevant participant characteristics (including animal populations), independent variables (experimental manipulations, treatments, or interventions), ruling out of possible confounding variables, dependent variables (outcomes, criterion), and other features of study designs
* Method(s) of synthesis and if meta-analysis was used, the specific methods used to integrate studies (e.g., effect-size metric, averaging method, the model used in homogeneity analysis)"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

**RQ1)** How is teachers’ technological-pedagogical content knowledge (TPACK) conceptualized within research? What different components are defined and on which component does the focus lie (T, P, C, TP, TC, TP, PC, TPC)? 

**RQ1a)** What kind of test instruments have been used to measure TPCK in empirical studies and in which ways to the differ in their application? 

**RQ2)** How do the several existing TPCK measurement instruments mirror the distinct conceptualizations of TPCK? 



# Methods


## Eligibility: Inclusion and Exclusion Criteria

<button data-toggle="collapse" data-target="#eiaec">show sources</button>
<div id="eiaec" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Specify the study characteristics (such as PICO, study design, setting, time frame) and report characteristics (such as years considered, language, publication status) to be used as criteria for eligibility for the review",
                                            # PROSPERO
                                            "Give details of the types of study (study designs) eligible for inclusion in the review. If there are no restrictions on the types of study design eligible for inclusion, or certain study types are excluded, this should be stated. The preferred format includes details of both inclusion and exclusion criteria.",
                                            # MARS
                                            "Describe the criteria for selecting studies, including

* Independent variables (e.g., experimental manipulations, types of treatments or interventions or predictor variables)
* Dependent variable (e.g., outcomes, in syntheses of clinical research including both potential benefits and potential adverse effects)
* Eligible study designs (e.g., methods of sampling or treatment assignment)
* Handling of multiple reports about the same study or sample, describing which are primary and handling of multiple measures using the same participants
* Restrictions on study inclusion (e.g., by study age, language, location, or report type)
* Changes to the prespecified inclusion and exclusion criteria, and when these changes were made
* Handling of reports that did not contain sufficient information to judge eligibility (e.g., lacking information about study design) and reports that did not include sufficient information for analysis (e.g., did not report numerical data about those outcomes)"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

### Inclusion criteria


* Papers that investigate teachers’ professional knowledge for technology-enhanced teaching based on the TPACK framework by Mishra & Koehler  (2006) or extensions thereof

* Theoretical contributions that conceptualize TPACK (or adoptions thereof)

* Empirical studies that assess TPACK of teachers (either pre-service, trainee or in-service teachers, principals or teacher educators)

* Peer-reviewed journal articles, conference proceedings, book chapters and dissertations


### Exclusion criteria
 

* No fulltext available

* Papers that are not written in English

* Papers in which TPCK (or adaptions thereof) was not explicitly mentioned in the title or abstract

* Papers from which no clear conceptualization of TPCK can be made out (in the sense of RQ 2, see 2.2)


## Sources of Search: List and Rationale

<button data-toggle="collapse" data-target="#soslar">show sources</button>
<div id="soslar" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Searches: State the sources that will be searched. Give the search dates, and any restrictions (e.g. language or
publication period). Do NOT enter the full search strategy (it may be provided as a link or attachment.)",
                                            # MARS
                                            "Describe all information sources:

* Databases searched (e.g., PsycINFO, ClinicalTrials.gov), including dates of coverage (i.e., earliest and latest records included in the search), and software and search platforms used
* Names of specific journals that were searched and the volumes checked
* Explanation of rationale for choosing reference lists if examined (e.g., other relevant articles, previous research
syntheses)
* Documents for which forward (citation) searches were conducted, stating why these documents were chosen
* Number of researchers contacted if study authors or individual researchers were contacted to find studies or to obtain more information about included studies, as well as criteria for making contact (e.g., previous relevant publications), and response rate
* Dates of contact if other direct contact searches were conducted such as contacting corporate sponsors or mailings to distribution lists
* Search strategies in addition to those above and the results of these searches"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

* data bases:
  - Web of Science
  - PsychINFO
  - ERiC
  - ScienceDirect
  - ProQuest Dissertations
  - first 100 results from google scholar
* backwards search
  - After screening abstracts and titles: We use the three latest reviews on TPACK (or adaptions thereof) and screen their references


## Search Strategy

<button data-toggle="collapse" data-target="#searchs">show sources</button>
<div id="searchs" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Present draft of search strategy to be used for at least one electronic database, including planned limits, such that it could be repeated.",
                                            # PROSPERO
                                            "URL to search strategy: Give a link to a published pdf/word document detailing either the search strategy or an example of a search strategy for a specific database if available (including the keywords that will be used in the search strategies), or upload your search strategy. Do NOT provide links to your search results. Alternatively, upload your search strategy to CRD in pdf format. Please note that by doing so you are consenting to the file being made publicly accessible.",
                                            # MARS
                                            "Describe all information sources: Search strategies of electronic searches, such that they could be repeated (e.g., include the search terms used, Boolean connectors, fields searched, explosion of terms)."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

**Search String**

((TPACK OR TPCK  OR “technological pedagogical content knowledge”  OR “technological-pedagogical-content-knowledge"  OR "technological pedagogical and content knowledge")  AND teacher*)

**Additional Specifications use**

* language: English
* time span: 2005-2020

**Note**: In 2005, the TPACK model was first mentioned by Mishra and Koehler. Thus, to offer a complete picture on existing TPCK conceptualizations, all years since 2005 need to be taken into consideration. 

## Data Management Tools Used

<button data-toggle="collapse" data-target="#dmtu">show sources</button>
<div id="dmtu" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Describe the mechanism(s) that will be used to manage records and data throughout the review.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 


* Rayyan (https://rayyan.qcri.org/)
* Citavi (https://www.citavi.com/de)


## Data Extraction (Selection of Studies)

<button data-toggle="collapse" data-target="#desos">show sources</button>
<div id="desos" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "State the process that will be used for selecting studies (such as two independent reviewers) through each phase of the review (that is, screening, eligibility and inclusion in meta-analysis).",
                                            # PROSPERO
                                            "Data extraction (selection and coding): Describe how studies will be selected for inclusion. State what data will be extracted or obtained. State how this will be done and recorded.",
                                            # MARS
                                            "Describe the process for deciding which studies would be included in the syntheses and/or included in the meta-analysis, including

* Document elements (e.g., title, abstract, full text) used to make decisions about inclusion or exclusion from the synthesis at each step of the screening process 
* Qualifications (e.g., training, educational or professional status) of those who conducted each step in the study selection process, stating whether each step was conducted by a single person or in duplicate as well as an explanation of how reliability was assessed if one screener was used and how disagreements were resolved if multiple were used."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

Two independent reviewers conduct every of the following steps:

  1)	screening titles and if we cannot make a statement based on the title we will screen the abstract
  2)	screening all abstracts
  3)	screening full texts

At each of this three steps articles will be included if the inclusion criteria apply and none of the exclusivity criteria apply. If this is not the case, articles will be excluded. If it is not clear whether articles should be included or excluded, these studies will be labelled as “maybe” and then discussed until consens is reached among the raters. Articles will also be discussed together if there are disagreements. These disagreements will be resolved by discussing the article in detail until consens is reached. If no consens can be reached, another independent reviewer will be brought in for discussion.



## Method of Extracting Data & Information (from Reports)

<button data-toggle="collapse" data-target="#edfr">show sources</button>
<div id="edfr" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Describe planned method of extracting data from reports (such as piloting forms, done independently, in duplicate), any processes for obtaining and confirming data from investigators.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Describe methods of extracting data from reports, including 

* Variables for which data were sought and the variable categories 
* Qualifications of those who conducted each step in the data extraction process, stating whether each step was conducted by a single person or in duplicate and an explanation of how reliability was assessed if one screener was used and how disagreements were resolved if multiple screeners were used as well as whether data coding forms, instructions for completion, and the data (including metadata) are available, stating where they can be found (e.g., public registry, supplemental materials)"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

* Studies will be coded in Rayyan by two independent raters using the detect duplicates, inclusion/exclusion/maybe and labeling function.

* To extract detailed information on the included studies, a standardized Excel or self-programmed dashboard that produces a relational database will be established and applied by two independent raters.

* All extracted data and information will be analyzed for inter-rater agreement and discrepancies will be discussed (see also 3.5).



## List and Description of Data and Information Extracted

<button data-toggle="collapse" data-target="#ladodaie">show sources</button>
<div id="ladodaie" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "
* List and define all variables for which data will be sought (such as PICO items, funding sources), any pre-planned data assumptions and simplifications
* List and define all outcomes for which data will be sought, including prioritization of main and additional outcomes, with rationale",
                                            # PROSPERO
                                            "
* Condition or domain being studied: Give a short description of the disease, condition or healthcare domain being studied. This could include health and wellbeing outcomes.
* Participants/population: Give summary criteria for the participants or populations being studied by the review. The preferred format includes details of both inclusion and exclusion criteria.
* Intervention(s), exposure(s): Give full and clear descriptions or definitions of the nature of the interventions or the exposures to be reviewed.
* Comparator(s)/control: Where relevant, give details of the alternatives against which the main subject/topic of the review will be compared (e.g. another intervention or a non-exposed control group). The preferred format includes details of both inclusion and exclusion criteria.
* Main and additional outcome(s): Give the pre-specified main (most important) outcomes of the review, including details of how the outcome is defined and measured and when these measurement are made, if these are part of the review inclusion criteria.
* Measures of effect: Please specify the effect measure(s) for you main outcome(s) e.g. relative risks, odds ratios, risk difference,
and/or 'number needed to treat.",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

* *General information on the publication*, such as publication status, publication year,  authors' names, type of paper (theoretical, empirical, ...)
* *Specific information on the authors*, such as discipline of the authors (general teacher educators, content specialists, didactical profession, ...)
* *In the case of empirical studies* : Sample Size, Sample Group (students, pre-service teachers, in-service teachers), country the study was conducted, Gender, subject domain, which kind of TPCK measurement was used (self-report, performance-based, observations,...)

Note: This list might be subject to change as we start with the revision process (see)


## Effect size transformation from individual studies

<button data-toggle="collapse" data-target="#estfis">show sources</button>
<div id="estfis" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Describe the statistical methods for calculating effect sizes, including the metric(s) used (e.g., correlation coefficients,
differences in means, risk ratios) and formula(s) used to calculate effect sizes."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

not possible as this is a review, not a meta-analysis


## Risk of Bias in Individual Studies

<button data-toggle="collapse" data-target="#robiis">show sources</button>
<div id="robiis" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS",
                                       "Added by authors"),
                            description = c(# PRISMA-P
                                            "Describe anticipated methods for assessing risk of bias of individual studies, including whether this will be done at the outcome or study level, or both; state how this information will be used in data synthesis",
                                            # PROSPERO
                                            "Risk of bias (quality) assessment: Describe the method of assessing risk of bias or quality assessment. State which characteristics of the studies will be assessed and any formal risk of bias tools that will be used.",
                                            # MARS
                                            "Describe any methods used to assess risk to internal validity in individual study results, including

* Risks assessed and criteria for concluding risk exists or does not exist
* Methods for including risk to internal validity in the decisions to synthesize of the data and the interpretation of results",
                                            # added by authors
                                            "Describe how the quality of original studies are rated. E.g. by 'The Study Design and Implementation Assessment Device (Study DIAD)': https://doi.org/10.1037/1082-989X.13.2.130"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

no issue

# Results


## Strategy for Data Synthesis

<button data-toggle="collapse" data-target="#sfds">show sources</button>
<div id="sfds" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "
* Describe criteria under which study data will be quantitatively synthesised.
* If data are appropriate for quantitative synthesis, describe planned summary measures, methods of handling data and methods of combining data from studies, including any planned exploration of consistency (such as I2, Kendall’s τ)
* If quantitative synthesis is not appropriate, describe the type of summary planned",
                                            # PROSPERO
                                            "Strategy for data synthesis: Provide details of the planned synthesis including a rationale for the methods selected. This must not be generic text but should be specific to your review and describe how the proposed analysis will be applied to your data.",
                                            # MARS
                                            "Describe narrative and statistical methods used to compare studies. If meta-analysis was conducted, describe the methods used to combine effects across studies and the model used to estimate the heterogeneity of the effects sizes (e.g., a fixed-effect, random-effects model robust variance estimation), including

* Rationale for the method of synthesis
* Methods for weighting study results
* Methods to estimate imprecision (e.g., confidence or credibility intervals) both within and between studies
* Description of all transformations or corrections (e.g., to account for small samples or unequal group numbers) and adjustments (e.g., for clustering, missing data, measurement artifacts, or construct-level relationships) made to the data and justification for these
* Additional analyses (e.g., subgroup analyses, meta-regression), including whether each analysis was prespecified or post hoc
* Selection of prior distributions and assessment of model fit if Bayesian analyses were conducted
* Name and version number of computer programs used for the analysis
* Statistical code and where it can be found (e.g., a supplement)"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

After selecting the sample used for analysis according to the selection process (see 3.5), each paper of the sample will be read carefully and the infomation (as outlined in 3.7) will be extracted and visualized in a table or diagram. A deeper analysis, that aims at answering the two research questions, will then be conducted for each of the papers from the sample.

