---
title: "Conceptualizations of the TPCK-Framework"
author:
- affiliation: University of Tübingen
  email: armin.fabian@uni-tuebingen.de
  name: Armin Fabian
  url: https://uni-tuebingen.de/de/175743
- affiliation: University of Tübingen
  email: iris.backfisch@uni-tuebingen
  name: Iris Backfisch
  url: https://uni-tuebingen.de/de/169665
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    highlight: espresso
    number_sections: yes
    theme: paper
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
description: "Synthesized from  \n"
css: www/style.css
---

```{r setup, echo=F, message=F, warning=F, comment=F}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(pander)
library(dplyr)
library(kableExtra)
```

\
\
\

<div style="padding: 5px; background-color: #F0F0F0;">
__This is__ a Rmd-template for protocols and reporting of systematic reviews and meta-analyses. It synthesizes three sources of standards:

* [PRISMA-P](https://doi.org/10.1136/bmj.i4086)
* [PROSPERO](https://www.crd.york.ac.uk/prospero/)
* [MARS](https://doi.org/10.1037/amp0000389)

The template is __aimed at__

* guiding the process of planning the systemtic review/ meta-analysis
* providing a form for preregistration (enter your text, export as standalone html, upload as preregistration)

We are aware that MARS targets aspects of reporting after the systemtic review/ meta-analysis is completed rather than decisions and reasoning in the planning phase as PRISMA-P and PROSPERO. MARS nevertheless provides a good framework to determine crucial points for systemtic reviews/ meta-analyses to be addressed as early as in the planning phase.
</div>

  
_Standards have been partially adapted. Click 'show changes' to see changes and reasons for change._  

<button data-toggle="collapse" data-target="#changes">show changes</button>
<div id="changes" class="collapse">
| standard |  implemented change  | reason                      |
|:---------|:---------------------|:----------------------------|
| MARS |  Left out paper section "Abstract"  |  An abstract is important for reporting, not however, for planning and registering. |
| MARS |  Left out paper section "Results" and parts of "Discussion"  |  Specifications on how to report results is important for reporting, not however, for planning and registering. Prospective information on how results will be computed/ synthesized is preserved. |
| MARS | Left out "Protocol: List where the full protocol can be found" | This form practically is the protocol. |
|  PROSPERO  |  Left out non-mandatory fields or integrated them with mandatory fields.  |  Avoiding too detailed specifications. All relevant informations will be integrated. |
| PROSPERO | Left out some options in "Type and method of review" | Options left out are purely health/ medicine related. |
| PROSPERO | Left out "Health area of the review" | This field is purely health/ medicine related. |


</div>

\
\
\


# General 

## Working Title

<button data-toggle="collapse" data-target="#wt">show sources</button>
<div id="wt" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Identify the report as a protocol of a systematic review. If the protocol is for an update of a previous systematic review, identify as such",
                                            # PROSPERO
                                            "Give the working title of the review, for example the one used for obtaining funding. Ideally the title should state succinctly the interventions or exposures being reviewed and the associated health or social problems. Where appropriate, the title should use the PI(E)COS structure to contain information on the Participants, Intervention (or Exposure) and Comparison groups, the Outcomes to be measured and Study designs to be included.

For reviews in languages other than English, this field should be used to enter the title in the language of the
review. This will be displayed together with the English language title.",
                                            # MARS
                                            "Title: State the research question and type of research synthesis (e.g., narrative synthesis, meta-analysis)"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

Bringing Light Into the Dark: A Systematic Review on the Diverse Conceptualizations of the TPCK Framework


## Type of Review

<button data-toggle="collapse" data-target="#typeor">show sources</button>
<div id="typeor" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Type and method of review: Select the type of review and the review method from the lists below. Select the health area(s) of interest for your review.

* Meta-analysis
* Narrative synthesis
* Network meta-analysis
* Review of reviews
* Synthesis of qualitative studies
* Systematic review
* Other",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

Systematic Review



## Link to Registration

<button data-toggle="collapse" data-target="#ltr">show sources</button>
<div id="ltr" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "If registered, provide the name of the registry (such as PROSPERO) and registration number.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Give the place where the synthesis is registered and its registry number, if registered"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

This form is used as registration


## Anticipated start and completion date

<button data-toggle="collapse" data-target="#aasd">show sources</button>
<div id="aasd" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Give the date when the systematic review commenced, or is expected to commence. Give the date by which the review is expected to be completed.",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

**Start**: September 2020 

**Anticipated Complection Date**: Februrary 2021



## Stage of Review

<button data-toggle="collapse" data-target="#sor">show sources</button>
<div id="sor" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Indicate the stage of progress of the review by ticking the relevant Started and Completed boxes. Additional
information may be added in the free text box provided.
Please note: Reviews that have progressed beyond the point of completing data extraction at the time of
initial registration are not eligible for inclusion in PROSPERO. Should evidence of incorrect status and/or
completion date being supplied at the time of submission come to light, the content of the PROSPERO
record will be removed leaving only the title and named contact details and a statement that inaccuracies in
the stage of the review date had been identified.
This field should be updated when any amendments are made to a published record and on completion and
publication of the review. If this field was pre-populated from the initial screening questions then you are not
able to edit it until the record is published.

* The review has not yet started: [yes/no]

| Review stage | Started | Completed |
|:--------------------------------------------| :----:| :----:|
| Preliminary searches | Yes/No | Yes/No
| Piloting of the study selection process | Yes/No | Yes/No
| Formal screening of search results against eligibility criteria | Yes/No | Yes/No
| Data extraction | Yes/No | Yes/No
| Risk of bias (quality) assessment | Yes/No | Yes/No
| Data analysis | Yes/No | Yes/No

Provide any other relevant information about the stage of the review here (e.g. Funded proposal, protocol not
yet finalised).",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources, escape = F) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

The review has not yet started [yes/no]: no

| Review stage | Started | Completed |
|:--------------------------------------------| :----:| :----:|
| Preliminary searches | Yes | No
| Piloting of the study selection process | No | No
| Formal screening of search results against eligibility criteria | No | No
| Data extraction | No | No
| Risk of bias (quality) assessment | No | No
| Data analysis | No | No


## Names, Affiliations, Contact

<button data-toggle="collapse" data-target="#nac">show sources</button>
<div id="nac" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "
* Provide name, institutional affiliation, e-mail address of all protocol authors; provide physical mailing address of corresponding author.
* Describe contributions of protocol authors and identify the guarantor of the review.",
                                            # PROSPERO
                                            "
* Named Contact: The named contact acts as the guarantor for the accuracy of the information presented in the register record.
* Named contact email: Give the electronic mail address of the named contact.
* Organisational affiliation of the review: Full title of the organisational affiliations for this review and website address if available. This field may be completed as 'None' if the review is not affiliated to any organisation.
* Review team members and their organisational affiliations: Give the personal details and the organisational affiliations of each member of the review team. Affiliation refers to groups or organisations to which review team members belong.",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._

## Collaborators

<button data-toggle="collapse" data-target="#colla">show sources</button>
<div id="colla" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Collaborators (name & affilitation) of individuals working on the review, but are not review team member.",
                                            # MARS
                                            "Not specified."))
# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

* Named contact: Armin Fabian
* Named contact email: armin.fabian@uni-tuebingen.de
* Named contact ORCID: [0000-0001-6493-2147](https://orcid.org/0000-0001-6493-2147)
* Organisational affiliation of the review: University of Tübingen, Germany
* Review team members and their organisational affiliations:
  - Iris Backfisch, i.backfisch@iwm-tuebingen.de ORCID [0000-0002-1363-9888](https://orcid.org/0000-0002-1363-9888)


## Amendments to previous versions

<button data-toggle="collapse" data-target="#atpv">show sources</button>
<div id="atpv" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "If the protocol represents an amendment of a previously completed or published protocol, identify as such and list changes; otherwise, state plan for documenting important protocol amendments.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

Amendments will be published as new version of the document under the same DOI (or will point to previous version).


## Funding sources, sponsors and their roles

<button data-toggle="collapse" data-target="#fsign">show sources</button>
<div id="fsign" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "
* Indicate sources of financial or other support for the review
* Provide name for the review funder and/or sponsor
* Describe roles of funder(s), sponsor(s), and/or institution(s), if any, in developing the protocol",
                                            # PROSPERO
                                            "Funding sources/sponsors: Give details of the individuals, organizations, groups or other legal entities who take responsibility for initiating, managing, sponsoring and/or financing the review. Include any unique identification numbers assigned to the review by the individuals or bodies listed. Grant numbers.",
                                            # MARS
                                            "
* List all sources of monetary and in-kind funding support
* State the role of funders in conducting the synthesis and deciding to publish the results, if any"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

No external funding.


## Conflict of Interest

<button data-toggle="collapse" data-target="#coi">show sources</button>
<div id="coi" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "List any conditions that could lead to actual or perceived undue influence on judgements concerning the main topic investigated in the review.",
                                            # MARS
                                            "Describe possible conflicts of interest, including financial and other nonfinancial interests."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

No conflict of interest.


# Introduction

## Rationale

<button data-toggle="collapse" data-target="#ram">show sources</button>
<div id="ram" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Describe the rationale for the review in the context of what is already known.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Problem: State the question or relation(s) under investigation, including

* Historical background, including previous syntheses and meta-analyses related to the topic 
* Theoretical, policy, and/or practical issues related to the question or relation(s) of interest
* Populations and settings to which the question or relation(s) is relevant
* Rationale for
   (a) choice of study designs, 
   (b) the selection and coding of outcomes, 
   (c) the selection and coding potential moderators or mediators of results 
* Psychometric characteristics of outcome measures and other variables
"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

When it comes to school or education as such, the discussion about the use of digital media has become ubiquitous. However, recent studies indicate that teachers still rarely use digital technologies for educational purposes, and if they do, they rarely integrate them into teaching in a didactically meaningful manner (Farjon, Smits & Voogt, 2019). For years, protagonists of the school system as well as researchers in the field have tried to identify possible boundary conditions that hinder or foster teachers in their intentions to use digital technologies  in classrooms (Farjon, Smits, & Voogt, 2019; Knezek & Christensen, 2016; Petko, 2012). It is commonly assumed that one such boundary condition is the professional knowledge of teachers (Kunter et al., 2013; Baumert et al., 2010; Shulman, 1987). Accordingly, to use technologies in classrooms purposefully, teachers need specific knowledge that is tailored around the use of digital technologies. To better understand such technology-related teaching knowledge, researchers around the globe have established a variety of diverse conceptual models. One of the most recited and adopted models, that has guided researchers throughout the last decade in conceptualizing teachers’ professional knowledge, is the TPACK (**t**echnological, **p**edagogical and **c**ontent **k**nowledge) model by Mishra and Koehler (2006). The TPACK model captures the idea of bringing together and connecting basic knowledge components (i. e. knowledge about technology, pedagogy and content) to form a new central form of knowledge – TPCK. In literature, TPCK has evolved to become the central focus of researchers when it comes to technology integration (Kim & Lee, 2018).  Even though, the TPACK model’s underlying structure remains open for discussion (Cox & Graham, 2009; Willermark, 2018), there is increasing consensus among researchers that TPCK is the form of knowledge which constitutes *the* essential prerequisite for teachers who intent to enhance their teaching with the help of digital technologies. 

Ever since the introduction of the TPACK model in 2006, numerous researchers have worked *on* the model trying to clarify its underlying structure (Angeli & Valanides, 2009; Graham, 2011); or *with* the model using it as theoretical background for data driven studies (Angeli et al., 2016; Cavanagh & Koehler, 2013;). The question of what TPCK constitutes is of particular interest and has thus driven many researchers in their endeavours to make sense of this complex and multifaceted model (see e. g. Niess, Gollow-Wiles, & Angeli, 2019 for an overview). Yet, to date the question of what TPCK is remains a source of scholarly debate (Voogt et al., 2013). Most fruitful contributions to this debate stem from systematic reviews as they help to guide researchers through the seemingly obscure jungle of TPACK literature. Whereas most review authors have tried to collect, connect and link existing TPCK conceptualisations through existing papers (e.g. Voogt et al., 2013), others have focused on categorizing measurement instruments that had been put to practice in date-driven studies in the past (Abbitt, 2011; Koehler, Shin & Mishra, 2012). 

However, in examining existing reviews as well as recent TPACK papers, two (closely linked) fundamental desiderates become apparent. First, reviews so far focused on either tackling the dichotomous debate that surrounds TPACK (i. e. *transformative* vs. *integrative* view, see Angeli et al., 2016) or on categorizing TPACK measurement instruments (in categories such as performance based and self-assessment based, see De Rossi & Trevisan, 2018). To provide a comprehensive picture on TPCK, however, there is an urgent need to understand the different conceptualizations that researchers introduced when working on or with the TPACK model. Thus, to deliver interesting new insights to the vast and growing TPACK community, a systematic review that focuses on the diversity of possible conceptualizations of the TPACK model is essential. Second, researchers throughout the young TPACK history have pointed out that there is a general lack of focussing on subject-specific applications of the TPACK framework (e. g. Kramarski & Michalsky, 2010; Voogt et. al, 2013), which –in a way – contradicts the inherently content-specific feature of the TPACK model (as manifested through the “c” in TPCK). Instead, most TPCK researchers have seemed to use different focus lenses, such as technological or pedagogical ones, when applying the TPACK model as their guiding framework in their studies (De Rossi & Trevisan, 2018). 


Against this background, we conduct a systematic review that attempts to clarify and systematize existing conceptualizations within the huge corpus of TPACK research, with particular interest towards different foci lenses (i. e. subdomains of TPCK: TK, CK, PK, PCK, TCK, TPK and TPCK) that have been applied by researchers. As demanded for by several researchers, a special focus will hereby rely on how and to what extent content-specific features of TPACK were accounted for in the TPACK literature. To do so, we will also systematically look at existing methods to measure TPACK to map those against the diverse conceptualizations of TPACK. 

This systematic review will help to organize different approaches that researchers have taken and will take to understand and apply the highly complex framework of TPACK. 



## Research Questions

<button data-toggle="collapse" data-target="#rq">show sources</button>
<div id="rq" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Provide an explicit statement of the question(s) the review will address with reference to participants, interventions, comparators, and outcomes (PICO)",
                                            # PROSPERO
                                            "State the question(s) to be addressed by the review, clearly and precisely. Review questions may be specific or broad. It may be appropriate to break very broad questions down into a series of related more specific questions. Questions may be framed or refined using PI(E)COS where relevant.",
                                            # MARS
                                            "Objectives: State the hypotheses examined, indicating which were prespecified, including

* Question in terms of relevant participant characteristics (including animal populations), independent variables (experimental manipulations, treatments, or interventions), ruling out of possible confounding variables, dependent variables (outcomes, criterion), and other features of study designs
* Method(s) of synthesis and if meta-analysis was used, the specific methods used to integrate studies (e.g., effect-size metric, averaging method, the model used in homogeneity analysis)"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

**RQ1a)** How is teachers’ technological-pedagogical content knowledge (TPACK) conceptualized within research? What different components are defined and where does the focus lie?  

**RQ1b)** In particular, how much emphasisze is given on content-related features in data-driven studies as well as in theoretical contributions to the TPACK corpus that use the TPACK model as their guiding framework?

**RQ2)** How do the several existing TPACK measurement instruments mirror the distinct conceptualizations of TPACK? 



# Methods


## Eligibility: Inclusion and Exclusion Criteria

<button data-toggle="collapse" data-target="#eiaec">show sources</button>
<div id="eiaec" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Specify the study characteristics (such as PICO, study design, setting, time frame) and report characteristics (such as years considered, language, publication status) to be used as criteria for eligibility for the review",
                                            # PROSPERO
                                            "Give details of the types of study (study designs) eligible for inclusion in the review. If there are no restrictions on the types of study design eligible for inclusion, or certain study types are excluded, this should be stated. The preferred format includes details of both inclusion and exclusion criteria.",
                                            # MARS
                                            "Describe the criteria for selecting studies, including

* Independent variables (e.g., experimental manipulations, types of treatments or interventions or predictor variables)
* Dependent variable (e.g., outcomes, in syntheses of clinical research including both potential benefits and potential adverse effects)
* Eligible study designs (e.g., methods of sampling or treatment assignment)
* Handling of multiple reports about the same study or sample, describing which are primary and handling of multiple measures using the same participants
* Restrictions on study inclusion (e.g., by study age, language, location, or report type)
* Changes to the prespecified inclusion and exclusion criteria, and when these changes were made
* Handling of reports that did not contain sufficient information to judge eligibility (e.g., lacking information about study design) and reports that did not include sufficient information for analysis (e.g., did not report numerical data about those outcomes)"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._

## Sources of Search: List and Rationale

<button data-toggle="collapse" data-target="#soslar">show sources</button>
<div id="soslar" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Searches: State the sources that will be searched. Give the search dates, and any restrictions (e.g. language or
publication period). Do NOT enter the full search strategy (it may be provided as a link or attachment.)",
                                            # MARS
                                            "Describe all information sources:

* Databases searched (e.g., PsycINFO, ClinicalTrials.gov), including dates of coverage (i.e., earliest and latest records included in the search), and software and search platforms used
* Names of specific journals that were searched and the volumes checked
* Explanation of rationale for choosing reference lists if examined (e.g., other relevant articles, previous research
syntheses)
* Documents for which forward (citation) searches were conducted, stating why these documents were chosen
* Number of researchers contacted if study authors or individual researchers were contacted to find studies or to obtain more information about included studies, as well as criteria for making contact (e.g., previous relevant publications), and response rate
* Dates of contact if other direct contact searches were conducted such as contacting corporate sponsors or mailings to distribution lists
* Search strategies in addition to those above and the results of these searches"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._


## Search Strategy

<button data-toggle="collapse" data-target="#searchs">show sources</button>
<div id="searchs" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Present draft of search strategy to be used for at least one electronic database, including planned limits, such that it could be repeated.",
                                            # PROSPERO
                                            "URL to search strategy: Give a link to a published pdf/word document detailing either the search strategy or an example of a search strategy for a specific database if available (including the keywords that will be used in the search strategies), or upload your search strategy. Do NOT provide links to your search results. Alternatively, upload your search strategy to CRD in pdf format. Please note that by doing so you are consenting to the file being made publicly accessible.",
                                            # MARS
                                            "Describe all information sources: Search strategies of electronic searches, such that they could be repeated (e.g., include the search terms used, Boolean connectors, fields searched, explosion of terms)."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._



## Data Management Tools Used

<button data-toggle="collapse" data-target="#dmtu">show sources</button>
<div id="dmtu" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Describe the mechanism(s) that will be used to manage records and data throughout the review.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._



## Data Extraction (Selection of Studies)

<button data-toggle="collapse" data-target="#desos">show sources</button>
<div id="desos" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "State the process that will be used for selecting studies (such as two independent reviewers) through each phase of the review (that is, screening, eligibility and inclusion in meta-analysis).",
                                            # PROSPERO
                                            "Data extraction (selection and coding): Describe how studies will be selected for inclusion. State what data will be extracted or obtained. State how this will be done and recorded.",
                                            # MARS
                                            "Describe the process for deciding which studies would be included in the syntheses and/or included in the meta-analysis, including

* Document elements (e.g., title, abstract, full text) used to make decisions about inclusion or exclusion from the synthesis at each step of the screening process 
* Qualifications (e.g., training, educational or professional status) of those who conducted each step in the study selection process, stating whether each step was conducted by a single person or in duplicate as well as an explanation of how reliability was assessed if one screener was used and how disagreements were resolved if multiple were used."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._


## Method of Extracting Data & Information (from Reports)

<button data-toggle="collapse" data-target="#edfr">show sources</button>
<div id="edfr" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Describe planned method of extracting data from reports (such as piloting forms, done independently, in duplicate), any processes for obtaining and confirming data from investigators.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Describe methods of extracting data from reports, including 

* Variables for which data were sought and the variable categories 
* Qualifications of those who conducted each step in the data extraction process, stating whether each step was conducted by a single person or in duplicate and an explanation of how reliability was assessed if one screener was used and how disagreements were resolved if multiple screeners were used as well as whether data coding forms, instructions for completion, and the data (including metadata) are available, stating where they can be found (e.g., public registry, supplemental materials)"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._



## List and Description of Data and Information Extracted

<button data-toggle="collapse" data-target="#ladodaie">show sources</button>
<div id="ladodaie" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "
* List and define all variables for which data will be sought (such as PICO items, funding sources), any pre-planned data assumptions and simplifications
* List and define all outcomes for which data will be sought, including prioritization of main and additional outcomes, with rationale",
                                            # PROSPERO
                                            "
* Condition or domain being studied: Give a short description of the disease, condition or healthcare domain being studied. This could include health and wellbeing outcomes.
* Participants/population: Give summary criteria for the participants or populations being studied by the review. The preferred format includes details of both inclusion and exclusion criteria.
* Intervention(s), exposure(s): Give full and clear descriptions or definitions of the nature of the interventions or the exposures to be reviewed.
* Comparator(s)/control: Where relevant, give details of the alternatives against which the main subject/topic of the review will be compared (e.g. another intervention or a non-exposed control group). The preferred format includes details of both inclusion and exclusion criteria.
* Main and additional outcome(s): Give the pre-specified main (most important) outcomes of the review, including details of how the outcome is defined and measured and when these measurement are made, if these are part of the review inclusion criteria.
* Measures of effect: Please specify the effect measure(s) for you main outcome(s) e.g. relative risks, odds ratios, risk difference,
and/or 'number needed to treat.",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._


## Effect size transformation from individual studies

<button data-toggle="collapse" data-target="#estfis">show sources</button>
<div id="estfis" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Not specified.",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Describe the statistical methods for calculating effect sizes, including the metric(s) used (e.g., correlation coefficients,
differences in means, risk ratios) and formula(s) used to calculate effect sizes."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._


## Risk of Bias in Individual Studies

<button data-toggle="collapse" data-target="#robiis">show sources</button>
<div id="robiis" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS",
                                       "Added by authors"),
                            description = c(# PRISMA-P
                                            "Describe anticipated methods for assessing risk of bias of individual studies, including whether this will be done at the outcome or study level, or both; state how this information will be used in data synthesis",
                                            # PROSPERO
                                            "Risk of bias (quality) assessment: Describe the method of assessing risk of bias or quality assessment. State which characteristics of the studies will be assessed and any formal risk of bias tools that will be used.",
                                            # MARS
                                            "Describe any methods used to assess risk to internal validity in individual study results, including

* Risks assessed and criteria for concluding risk exists or does not exist
* Methods for including risk to internal validity in the decisions to synthesize of the data and the interpretation of results",
                                            # added by authors
                                            "Describe how the quality of original studies are rated. E.g. by 'The Study Design and Implementation Assessment Device (Study DIAD)': https://doi.org/10.1037/1082-989X.13.2.130"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._


# Results


## Strategy for Data Synthesis

<button data-toggle="collapse" data-target="#sfds">show sources</button>
<div id="sfds" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "
* Describe criteria under which study data will be quantitatively synthesised.
* If data are appropriate for quantitative synthesis, describe planned summary measures, methods of handling data and methods of combining data from studies, including any planned exploration of consistency (such as I2, Kendall’s τ)
* If quantitative synthesis is not appropriate, describe the type of summary planned",
                                            # PROSPERO
                                            "Strategy for data synthesis: Provide details of the planned synthesis including a rationale for the methods selected. This must not be generic text but should be specific to your review and describe how the proposed analysis will be applied to your data.",
                                            # MARS
                                            "Describe narrative and statistical methods used to compare studies. If meta-analysis was conducted, describe the methods used to combine effects across studies and the model used to estimate the heterogeneity of the effects sizes (e.g., a fixed-effect, random-effects model robust variance estimation), including

* Rationale for the method of synthesis
* Methods for weighting study results
* Methods to estimate imprecision (e.g., confidence or credibility intervals) both within and between studies
* Description of all transformations or corrections (e.g., to account for small samples or unequal group numbers) and adjustments (e.g., for clustering, missing data, measurement artifacts, or construct-level relationships) made to the data and justification for these
* Additional analyses (e.g., subgroup analyses, meta-regression), including whether each analysis was prespecified or post hoc
* Selection of prior distributions and assessment of model fit if Bayesian analyses were conducted
* Name and version number of computer programs used for the analysis
* Statistical code and where it can be found (e.g., a supplement)"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._


## Moderators/ Subgroups

<button data-toggle="collapse" data-target="#modarat">show sources</button>
<div id="modarat" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Describe any proposed additional analyses (such as sensitivity or subgroup analyses, meta-regression)",
                                            # PROSPERO
                                            "Analysis of subgroups or subsets: State any planned investigation of ‘subgroups’. Be clear and specific about which type of study or participant will be included in each group or covariate investigated. State the planned analytic approach.",
                                            # MARS
                                            "Not specified."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._



## Assessment of Publication Bias

<button data-toggle="collapse" data-target="#aopb">show sources</button>
<div id="aopb" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Specify any planned assessment of meta-bias(es) (such as publication bias across studies, selective reporting within studies)",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Describe risk of bias across studies, including

* Statement about whether
   (a) unpublished studies and unreported data, or 
   (b) only published data were included in the synthesis and the rationale if only published data were used
* Assessments of the impact of publication bias (e.g., modeling of data censoring, trim-and-fill analysis)
* Results of any statistical analyses looking for selective reporting of results within studies"))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._


# Discussion


## Strength of Evidence

<button data-toggle="collapse" data-target="#stroe">show sources</button>
<div id="stroe" class="collapse">

```{r}
# avoiding markdown tables because they're not exactly the prettiest flower in the bunch
# set up the table
table_sources <- data.frame(source = c("PRISMA-P",     # first column will be always the same
                                       "PROSPERO", 
                                       "MARS"),
                            description = c(# PRISMA-P
                                            "Describe how the strength of the body of evidence will be assessed (such as GRADE).",
                                            # PROSPERO
                                            "Not specified.",
                                            # MARS
                                            "Describe the generalizability (external validity) of conclusions, including • Implications for related populations, intervention variations, dependent (outcome) variables."))

# produce table
knitr::kable(table_sources) %>%
    kable_styling(fixed_thead = T) %>%
    column_spec(1, bold = T) %>%
    row_spec(0, background = "#ececec")
```

</div> 

_Put your text here._